---
title: "Model_3"
author: "Ian Brogan"
date: "5/7/2020"
output: html_document
---

# Setup
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)

ecommerce <- as.data.frame(read_rds("C:/Users/Ian Brogan/Desktop/Willamette Stuff/Spring 2020/ML/ecommerce.rds") %>%
  rowid_to_column("id"))
```

# Data Exploration

```{r}
glimpse(ecommerce)
```

```{r}
max(ecommerce$final_total)
min(ecommerce$final_total)
mean(ecommerce$final_total)
```

```{r}
ecommerce %>%
  count(final_total) %>%
  arrange(desc(n))
```
A lot of 25 dollar purchases, and 21.16.

```{r}
ecommerce %>%
  group_by(repeat_customer) %>%
  summarise_at(vars(-product_details, -date, -id), funs(mean(., na.rm=TRUE)))
```
So the average final total for repeat customers is $23.00 more than that of non-repeat customers.

```{r}
ecommerce %>%
  count(repeat_customer)
  
```

We are also dealing with *A LOT* more FALSE than TRUE. 

# Getting Some Top Words From Data

```{r}
library(tidytext)
data(stop_words)
```
```{r}
top_words <- ecommerce %>%
  unnest_tokens(word, product_details) %>%
  anti_join(stop_words) %>% 
  filter(!(word %in% c("Product Name:", "[Pp]roduct"))) %>% 
  count(id, word) %>% 
  group_by(id) %>% 
  mutate(exists = if_else(n>0,1,0)) %>%
  ungroup %>% 
  right_join(ecommerce, by="id") %>%
  count(repeat_customer, word) %>% 
  group_by(repeat_customer) %>% 
  top_n(10,n) %>%
  ungroup %>% 
  select(word) %>% 
  distinct()

top_words
```

# PCA
## Setup
```{r}
comm_words <- ecommerce %>% 
  unnest_tokens(word, product_details) %>%
  anti_join(stop_words) %>%
  filter(!(word %in% c("Product Name:", "[Pp]roduct"))) %>% #get rid of these words
  count(id, word) %>% 
  group_by(word) %>% 
  mutate(total = sum(n)) %>% 
  filter(total > 500) %>% #words that only show up more than 500 times
  ungroup %>% 
  group_by(id) %>% 
  mutate(exists = if_else(n>0,1,0)) %>% 
  ungroup %>% 
  pivot_wider(id_cols = id, names_from = word, values_from = exists, values_fill = c(exists=0)) %>% 
  right_join(ecommerce, by="id") %>% 
  replace(.,is.na(.),0) %>% 
  select(-id, -date, -product_details, -final_total) 
```
```{r}
names(comm_words)
```

## Run the principle component analysis

```{r}
pr_ecomm <- prcomp(x = select(comm_words,-repeat_customer), scale = F, center = T)
summary(pr_ecomm)
```

```{r}
screeplot(pr_ecomm, type = "lines")
```

Talk about a clear scree plot...

## Visualize biplots

```{r}
biplot(pr_ecomm)
biplot(pr_ecomm, choices = c(1,2))
```

## Factor loadings

```{r}
pr_ecomm$rotation
```

```{r}
head(pr_ecomm$x)
```

## Add variety label to principle components and name them

```{r}
prc_ecomm <- bind_cols(select(comm_words, repeat_customer),as.data.frame(pr_ecomm$x)) %>% 
  select(1:30) 
```
```{r}
head(prc_ecomm)
```

```{r}
prc_ecomm<- prc_ecomm %>%
  mutate(repeat_customer = as.character(repeat_customer))
library(caret)
fit <- train(repeat_customer ~ .,
             data = prc_ecomm, 
             method = "naive_bayes",
             metric = "Kappa",
             trControl = trainControl(method = "cv"))
confusionMatrix(predict(fit, prc_ecomm),factor(prc_ecomm$repeat_customer))
```
